Manuscript Figures for Genome Biology

### 2019-03-28 manuscript_figures/manuscript_figures_main.Rmd
fix x-axis label

r1.1a <- r1.1a +
  geom_point(data=res5d.sum, aes(x = value.x, y = value.y, 
             shape = control), size = 3.5) +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 19, size = 2.5, color = "white") +
  scale_shape_manual(values = c(1, 19)) + 
  ggtitle("In silico experiments") +
  scale_x_continuous(expression(paste(bold(alpha), bold(" level"))),
                         breaks=seq(0, 1, by=0.02))
```

@@

r1.1b <- r1.1b +
  geom_point(data=res5d.sum, aes(x = value.x, y = value.y, 
             shape = control), size = 3.5) +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 19, size = 2.5, color = "white") +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 1, size = 3.5) +
  scale_shape_manual(values = c(1, 19)) +
  ggtitle("Polyester") +
  scale_x_continuous(expression(paste(bold(alpha), bold(" level"))),
                         breaks=seq(0, 1, by=0.02))
```

>>>>

r1.1a <- r1.1a +
  geom_point(data=res5d.sum, aes(x = value.x, y = value.y, 
             shape = control), size = 3.5) +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 19, size = 2.5, color = "white") +
  scale_shape_manual(values = c(1, 19)) + 
  ggtitle("In silico experiments") +
  scale_x_continuous(breaks=seq(0, 1, by=0.02))
```

@@

r1.1b <- r1.1b +
  geom_point(data=res5d.sum, aes(x = value.x, y = value.y, 
             shape = control), size = 3.5) +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 19, size = 2.5, color = "white") +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 1, size = 3.5) +
  scale_shape_manual(values = c(1, 19)) +
  ggtitle("Polyester") +
  scale_x_continuous(breaks=seq(0, 1, by=0.02))
```
